\documentclass[12pt]{article}
\title{REPORT}
\author{RUBEL CHOWDHURY}
\begin{document}
 \textbf{\\ \\ \\ \center PREMIER UNIVERSITY,CHITTAGONG \\}
 \textbf{DEPT. OF COMPUTER SCIENCE AND ENGINEERING}
 \maketitle
   \newpage
     \textsc{in the OOP lab we have learned below \\}
   \begin{itemize}
   \item[i]  Class \item[ii] Object \item[iii] Loop  \item[iv] enum \item[v] function \item[iv]Constructor \item[vi] Destructor \item[vii]inheritance
  \end{itemize}
  \bigskip \bigskip \bigskip \bigskip
   \paragraph{CLASS \\
   In the first lab we got a simple idea about CLASS.In this lab we learn about how to write a program with CLASS.Benefits of using  CLASS.}
  \paragraph{OBJECT\\
  In this lab we know about object.object is nothing but instance of class.like C struc object. 
  }
\paragraph{LOOP\\
IN this lab we also know about the loop.how to use loop in various way.
} 
   \paragraph{ENUM:\\
   In our second lab we learn about new topic enum.which is numbering type system.}
  \paragraph{Function\\
  In this second lab we also learn about function.How to declare a function and how to write it and call it another function. 
  } 
  \paragraph{Constructor:\\
   In this lab we have learned about Constructor and Destructor.How constructor and destructor works what the benefits of this.How the copy constructor works.}
    \paragraph{Operator overloading and Type conversation:\\
    In this lab we have learned operator overloading.Which operator can overload which can not.In this lab we have also known a new topic of programming named Type conversation.How can we conversation one to another.}
    \paragraph{Inheritance:\\
    In this lab we have known about the uses of Inheritance.How can we derived a class.what is it`s importance}
    \bigskip \bigskip
  \textsl{\\ \\ \\ \\ \center THE END \\}
 \end{document}