\documentclass[12pt]{article}
\title{LAB REPORT}
\author{Suddam}
\begin{document}

\textbf{\bigskip \bigskip \bigskip \bigskip}
\begin{Large}
\begin{center}
\textbf{\\ \bigskip PREMIER UNIVERSITY,CHITTAGONG } \\
\textbf{DEPT. OF COMPUTER SCIENCE AND ENGINEERING}\\
\end{center}
\end{Large}
\maketitle
\newpage
 \begin{center}
   \textbf{1st Lab} \\
 \end{center} 
 We learn from First lab below: 
 \begin{itemize} 
 \item Object. \item Class. \item Using of loop.
 \end{itemize}
  Object:\\ 
  {In this lab we know about object. Object is nothing but instance of class. Like C struck object. } \\ \\
   {Class: \\ 
   We got a simple idea about Class. In this lab we learn about how to write a program with Class. Benefits of using Class.} \\ \\
    {Loop:\\
     In this lab we also know about the Loop. How to use loop in various way. } \\ \\ \\
      \begin{large}
       We Practice programming problems on this. \\ 
       \end{large} 
       \begin{center}
        \textbf{2nd Lab} \\
         \end{center}
          We learn from Second lab below:
           \begin{itemize}
            \item Enum. \item Function. 
            \end{itemize}
             Enum : \\ 
             We learn about new topic Enum. Which is numbering type system. \\ \\
              Function:\\ 
              We also learn about function. How to declare a function and how to write it and call it another function. \\ \\ 
              \begin{large}
               We Practice programming problems on this. \\
                \end{large}
                 \newpage
                  \begin{center}
                   \textbf{3rd Lab} 
                   \end{center} We learn from Third lab below: 
                   \begin{itemize}
                    \item Default argument.
                     \item function overloading. \item Inline function.
                      \end{itemize}
                       Default argument: \\ 
                       In this lab we know OOP's topic default argument.\\ \\ 
                       Function overloading:\\
                        Function overloading is the most important lesson for OOP. In C language we didn't found function overloading but in C++.\\ \\
                         Inline Function:\\
                          How to work Inline function in program.\\ \\
                           \begin{large} We Practice programming problems on this. \\ 
                           \end{large}\\ \\ \\ \\ \\ 
                           \begin{center}
                            \begin{large} 
                            Other Labs.\\

\begin{tabular}{|l|r|c|} \hline
 Lab 4& Practice programming problems & Find solution \\ \hline\
  Lab 5& Practice programming problems & Find solution \\ \hline 
  Lab 6& Practice programming problems & Find solution \\ \hline 
  Lab 7& Practice programming problems & Find solution \\ \hline

\end{tabular} 
\end{large}

 \end{center}
  \end{document}